Solving the Nonstationary Richards Equation\\ With Adaptive $hp$-FEM

### 2011-03-15 paper.tex
few little corrections yet

Based on results of Section \ref{sec:hpfem}, we only use adaptive $hp$-FEM
for the computation. The relative spatial error tolerance in the $H^1$-norm
is set to $0.5 \%$. This quantity (ratio of spatial error estimate and 
solution norm) is used as stopping criterion for spatial mesh adaptivity

@@

This example is motivated by an existing nuclear waste repository for 
low- and intermediate-level waste. The name of the repository is {\em Richard} and it is situated %situated nahrazeno za located 
near Litom\v e\v rice, Czech Republic. The repository is located within a deep 
rock formation in the B{\'\i}dnice hill, 40~m below the surface and 70~m above 
the ground water table, and it is  surrounded by a tectonically fractured 
claystone. Under normal circumstances, this is a very stable unsaturated environment 
and so this is a typical problem for applying the Richards' equation model. 
In order to protect its surroundings from radiotoxic pollution, the repository is shielded 
with a 30~cm thick gravel layer that acts as a capillary barrier.  
%tahle veta mi prisla ok
% unsaturated hydraulic properties of gravel je opravdu ok formulace
The effect of the capillary barrier is based on unsaturated hydraulic properties of gravel.
%------
The unsaturated hydraulic conductivity of gravel reaches very high values 
at and near full saturation, but with decreasing saturation it falls steeply 
to almost zero values. Fig.~\ref{fig:cap-barrier-domain} depicts the repository 
scheme (more precisely just half of it since advantage is taken of
problem symmetry).

@@

\begin{equation}
\begin{split}
\int_{\Omega}  C(h^{n+1})\frac{h^{n+1} - h^n}{\Delta t}v_i \;{\rm
d}\bfx + \int_{\Omega} K(h^{n+1})\nabla h^{n+1} \cdot \nabla v_i \;{\rm
d}\bfx \\ - \int_{\Omega}K'(h^{n+1})\frac{\partial h^{n+1}}{\partial z}v_i \;{\rm
d}\bfx - \int_{\Gamma_N} g^{n+1} v_i \;{\rm d}\bfS = 0
\end{split}
\label{pavelfinal1}
\end{equation}
for all $i = 1, 2, \ldots, N$.
Here $N$ is the dimension of the finite element subspace of $V$,
the superscript $n$ enumerates time steps, $\Delta t$ is the length of the time step, 
and $\mathbf{f}$ stands for the contribution of the (generally time-dependent) 
Neumann boundary data.

>>>>

Based on results of Section \ref{sec:hpfem}, we only use adaptive $hp$-FEM
for the computation. The relative spatial error tolerance in the $H^1$-norm
is set to $0.5 \%$. This quantity (ratio of spatial error estimate and 
solution norm) is used as stopping criterion for spatial mesh adaptivity.

@@

This example is motivated by an existing nuclear waste repository for 
low- and intermediate-level waste. The name of the repository is {\em Richard} and it is situated %situated nahrazeno za located 
near Litom\v e\v rice, Czech Republic. The repository is located within a deep 
rock formation in the B{\'\i}dnice hill, 40~m below the surface and 70~m above 
the ground water table, and it is  surrounded by a tectonically fractured 
claystone. Under normal circumstances, this is a very stable unsaturated environment 
and so this is a typical problem for applying the Richards equation model. 
In order to protect its surroundings from radiotoxic pollution, the repository is shielded 
with a 30~cm thick gravel layer that acts as a capillary barrier.  
%tahle veta mi prisla ok
% unsaturated hydraulic properties of gravel je opravdu ok formulace
The effect of the capillary barrier is based on unsaturated hydraulic properties of gravel.
%------
The unsaturated hydraulic conductivity of gravel reaches very high values 
at and near full saturation, but with decreasing saturation it falls steeply 
to almost zero values. Fig.~\ref{fig:cap-barrier-domain} depicts the repository 
scheme (more precisely just half of it since advantage is taken of
problem symmetry).

@@

\begin{equation}
\begin{split}
\int_{\Omega}  C(h^{n+1})\frac{h^{n+1} - h^n}{\Delta t}v_i \;{\rm
d}\bfx + \int_{\Omega} K(h^{n+1})\nabla h^{n+1} \cdot \nabla v_i \;{\rm
d}\bfx \\ - \int_{\Omega}K'(h^{n+1})\frac{\partial h^{n+1}}{\partial z}v_i \;{\rm
d}\bfx - \int_{\Gamma_N} g^{n+1} v_i \;{\rm d}\bfS = 0
\end{split}
\label{pavelfinal1}
\end{equation}
for all $i = 1, 2, \ldots, N$.
Here $N$ is the dimension of the finite element subspace of $V$,
the superscript $n$ enumerates time steps, and $\Delta t$ is the length of the time step.
